The state learner -- a super learner for right-censored data

### 2025-01-13 manuscript/manuscript-lda.tex
split some equations

\institute{Anders Munch \at
              Section of Biostatistics, University of Copenhagen \\
              % Tel.: +123-45-678910\\
              % Fax: +123-45-678910\\
              \email{a.munch@sund.ku.dk}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
              \and %
              Thomas~A.~Gerds %
              \at Section of Biostatistics, University of Copenhagen }

@@

We introduce our notation and framework in Section~\ref{sec:framework}. In
Section~\ref{sec:super-learning} we define general super learning for
right-censored data. Section~\ref{sec:super-learner-simple} introduces the state
learner, and Section~\ref{sec:theor-results-prop} provides theoretical
guarantees. In Section~\ref{sec:targeted-learning} we discuss the use of the
state learner in the context of targeted learning. We report results of our
numerical experiments in Section~\ref{sec:numer-exper} and analyse a prostate
cancer data set in Section~\ref{sec:real-data-appl}.
Section~\ref{sec:discussion} contains a discussion of the merits and limitations
of our proposal. Proofs are given in the Appendix. An implementation of the
state learner is available at \url{https://github.com/amnudn/statelearner} along
with codes for reproducing our numerical experiments.

@@

  \quad \text{for all} \quad
  t \in [0,\tau],
  k \in \{-1,0,1,2\},
  x \in \mathcal{X}.

@@

@@

      =

@@

      \int_0^{\tau} \int_0^{s} w^a_n(s,u,\blank) [F - \hat{F}_n](u-, 0, \blank)[F - \hat{F}_n](s-, 0, \blank) F(\diff u, -1, \blank ) F ( \diff s, 1, \blank)

@@

An example of a targeted estimator is the one-step estimator, defined as
\begin{equation}
    \label{eq:one-step-def}
    \hat{\Psi}_{\text{OS}}(\data_n)
    =
    \tilde{\Psi}^0(\hat{a}_{1,n}(\data_n), \hat{a}_{2,n}(\data_n),
    H_n(\data_n))
    + \empmeas{[\psi(\blank; \hat{a}_{1,n}(\data_n), \hat{a}_{2,n}(\data_n),
      \hat{b}_n(\data_n) )]},
\end{equation}
where \( \empmeas \) is the empirical measure of a data set
\(\{O_i\}_{i=1}^n\).
Under suitable regularity conditions
we have the
following asymptotic expansion of the one-step estimator
\citep{pfanzagl1985contributions,van2003unified,fisher2021visually,kennedy2022semiparametric},
\begin{equation*}
  \hat{\Psi}_{\text{OS}}(\data_n)- \Psi(P)
  =  \empmeas{[\psi(\blank ; \Lambda_1, \Lambda_2, \Gamma)]}
  +\mathrm{Rem}{(\hat{\Lambda}_{1,n},\hat{\Lambda}_{2,n},  \hat{\Gamma}_n, P)} + \smallO_{P}(n^{-1/2}),
\end{equation*}
where the remainder term has the form
\begin{equation}
  \label{eq:4}
  \mathrm{Rem}{(\hat{\Lambda}_{1,n},\hat{\Lambda}_{2,n},  \hat{\Gamma}_n, P)}
  = \bigO_P{
    \left\{
      \|\Lambda_1-\hat{\Lambda}_{1,n}\|^2
      +
      \|\Lambda_2-\hat{\Lambda}_{2,n}\|^2
      +
      \|\Gamma-\hat{\Gamma}_{n}\|^2
    \right\}
  },
\end{equation}
for some suitable norm \( \|\blank \| \), for instance the
\( \mathcal{L}_{P}^2 \)-norm. When equation~(\ref{eq:4}) holds and the
nuisance parameters $\Lambda_1$, $\Lambda_2$, and $\Gamma$ are
consistently estimated at rate \( \smallO_P{(n^{-1/4})} \), then
\begin{equation}
  \label{eq:3}
  \sqrt{n}(\hat{\Psi}_{\text{OS}}(\data_n)- \Psi(P)) \weakly \mathcal{N}(0,
  P{[\psi(\blank; \Lambda_1, \Lambda_2, \Gamma)^2]}),
\end{equation}
where we use \( \weakly \) to denote weak convergence \citep{van2000asymptotic}.
In particular, equation~(\ref{eq:3}) and Slutsky's lemma imply that we can
obtain asymptotically valid \((1-\alpha)\cdot100\%\) confidence intervals by
calculating
\begin{equation*}
  \left[
    \hat{\Psi}_{\text{OS}}(\data_n) - q_{\alpha/2} \hat{\sigma}(\data_n) ,
    \;
    \hat{\Psi}_{\text{OS}}(\data_n) + q_{\alpha/2} \hat{\sigma}(\data_n)
  \right],
\end{equation*}
where \( q_{\alpha} \) is the \( (1-\alpha) \)-quantile of the standard normal
distribution and
\begin{equation*}
  \hat{\sigma}(\data_n)^2 = \empmeas{ \left[ \psi(\blank;
      \hat{a}_{1,n}(\data_n), \hat{a}_{2,n}(\data_n), \hat{b}_n(\data_n))^2
    \right]}.
\end{equation*}

@@

In the following we detail how the state learner can be used to
construct a targeted estimator of the cause-specific average treatment
effect \citep{rytgaard2022targeted}. We assume that the covariate
vector \( X \in \R^p \) contains a binary treatment indicator \( A \)
and a vector of potential confounders,
\( W \in \mathcal{W}\subset \R^{p-1} \).  We use $\mu$ to denote the
marginal distribution of \( W \) and $\pi$ to denote the conditional
probability of treatment,
\begin{equation*}
  \pi(w) = P(A=1 \mid W=w).
\end{equation*}
We assume throughout that $\pi$ is uniformly bounded away from \( 0 \)
and \( 1 \) on \( \mathcal{W} \) and that both \( A \) and \( W \) are
fully observed for all individuals. We use a super learner to
estimate $\pi$ \citep{Polley_Ledell_Kennedy_Laan_2023_Superlearn}, and
we denote this estimator by $\hat{\pi}_n$. We use the empirical
measure of \( \{W_1, \dots, W_n\} \) to estimate $\mu$, and denote
this estimator by $\hat{\mu}_n$. As parameter of interest we consider
the standardised difference in the absolute risk of an event with
cause 1 at time $\tau$:
\begin{equation*}
  \theta_{{\tau}}(Q) = \int_{\mathcal{W}} 
  \left\{
    \int_0^{\tau}
    S(s- \mid w, 1)  \Lambda_1(\diff s \mid w, 1)
    -
    \int_0^{\tau}
    S(s- \mid w, 0)  \Lambda_1(\diff s \mid w, 0)
  \right\}
  \mu(\diff w).
\end{equation*}
Under the usual assumptions for causal inference (consistency,
positivity, no unmeasured confounding) \( \theta_{{\tau}} \) can be
given the causal interpretation
\begin{equation*}
  \theta_{{\tau}}(Q) =
  P{(T^{1} \leq \tau, D^{1}=1)}-
  P{(T^{0} \leq \tau, D^{0}=1)},
\end{equation*}
where \( (T^a, D^a) \), \( a \in \{0,1\} \), denote potential outcomes
\citep{hernanRobinsWhatIf}. In this case, the interpretation of $\theta_{\tau}$
is the difference in the average risk of cause \( 1 \) occurring before time
\( \tau \) in the population if everyone had been given treatment (\( A=1 \))
compared to if no one had been given treatment \( (A=0) \).

Using equation~(\ref{eq:surv-def}) we may write
\( \theta_{{\tau}}(Q) = \tilde{\Psi}_{\tau}^0(\Lambda_1, \Lambda_2, \mu) \), where
\begin{equation}
  \label{eq:1}    
  \begin{split}
    \tilde{\Psi}_{\tau}^0(\Lambda_1, \Lambda_2, \mu)
    & =
      \int_{\mathcal{W}} 
      \int_0^{\tau}
      \exp{\{{-\Lambda_1(s- \mid w, 1)-\Lambda_2(s- \mid w, 1)}\}}  \Lambda_1(\diff s \mid
      w, 1)
      \mu(\diff w)
    \\
    &  \quad
      -\int_{\mathcal{W}} 
      \int_0^{\tau}
      \exp{\{{-\Lambda_1(s- \mid w, 0)-\Lambda_2(s- \mid w, 0)}\}}  \Lambda_1(\diff s \mid w, 0)
      \mu(\diff w).
  \end{split}
\end{equation}
The efficient influence function for the parameter $\tilde{\Psi}_{\tau}$ depends
on the set \( (\Lambda_1, \Lambda_2, \Gamma, \pi) \) of nuisance parameters.
We define
\begin{align*}
  \omega_a(A,W; \pi)
  &=  \frac{% (-1)^{a+1}
    \1{\{A=a\}}}{\pi(W)^{a}(1-\pi(W))^{1-a}},
  \\
  g(t, A, W; \Lambda_1, \Lambda_2)
  & = \int_0^{t}
    \exp{\{ {-\Lambda_1(s- \mid W, A)-\Lambda_2(s- \mid W, A)} \}}  \Lambda_1(\diff s \mid
    W, A),
  \\  
  M_j(\diff t \mid A, W;  \Lambda_j  )
  & = N_j(\diff t) -
    \1{\{\tilde{T} \geq t\}} \Lambda_j(\diff t \mid W, A),
    \quad j \in \{1,2\},
    \intertext{and}
    M(\diff t \mid A, W;  \Lambda_1, \Lambda_2  )
  & = M_1(\diff t \mid A, W;  \Lambda_1  ) +
    M_2(\diff t \mid A, W;  \Lambda_2  ).
\end{align*}
The efficient influence function can now be written as
\citep{van2003unified,jewell2007non,rytgaard2022targeted},
\begin{equation*}
  \psi_{\tau}(O; \Lambda_1, \Lambda_2, \Gamma, \pi)
  = \psi_{\tau}^1(O; \Lambda_1, \Lambda_2, \Gamma, \pi)
  - \psi_{\tau}^0(O; \Lambda_1, \Lambda_2, \Gamma, \pi)
  -\tilde{\Psi}_{\tau}^0(\Lambda_1, \Lambda_2, \mu),
\end{equation*}
where
\begin{equation}
  \label{eq:5}
  \begin{split}
    & \psi_{\tau}^a(O; \Lambda_1, \Lambda_2, \Gamma, \pi)
    \\
    & =
      \omega_a(A,W; \pi)
      \int_0^{\tau} \exp{\{{\Gamma(t- \mid A, W)}\}}   
      M_1(\diff t \mid A, W; \Lambda_1)
    \\
    & \quad
      -
      \omega_a(A,W; \pi)
      g(\tau, A, W; \Lambda_1, \Lambda_2)
    \\
    & \quad \quad \times
      \int_0^{\tau}
      \exp{\{{[\Gamma+\Lambda_1 + \Lambda_2](t- \mid A, W)}\}}
      M(\diff t \mid A, W; \Lambda_1, \Lambda_2)
    \\
    & \quad
      +
      \omega_a(A,W; \pi)      
      \int_0^{\tau}
      g(t, A, W; \Lambda_1, \Lambda_2)
    \\
    & \quad \quad \times
      \exp{\{{[\Gamma+\Lambda_1 + \Lambda_2](t- \mid A, W)}\}}
      M(\diff t \mid A, W; \Lambda_1, \Lambda_2)
    \\
    & \quad + g(\tau, a, W; \Lambda_1, \Lambda_2).
  \end{split}
\end{equation}
Equations~(\ref{eq:1}) and~(\ref{eq:5}) allow us to construct a one-step
estimator by using the definition given in equation~(\ref{eq:one-step-def}),
which gives the estimator
\begin{equation}
  \label{eq:one-step-comp-ate}
  \begin{split}
    \hat{\Psi}_{\tau,\text{OS}}(\data_n)
    = &
        \tilde{\Psi}_{\tau}^0(\hat{a}_1(\data_n), \hat{a}_2(\data_n),
        \hat{\mu}_n(\data_n))
    \\
      &
        +
        \empmeas{[\psi_{\tau}(\blank; \hat{a}_{1,n}(\data_n), \hat{a}_{2,n}(\data_n),
        \hat{b}_n(\data_n), \hat{\pi}_n(\data_n))]}
    \\
    = &
        \empmeas{[\psi_{\tau}^1(\blank; \hat{a}_{1,n}(\data_n), \hat{a}_{2,n}(\data_n),
        \hat{b}_n(\data_n), \hat{\pi}_n(\data_n))]}
    \\
      &
        - \empmeas{[\psi_{\tau}^0(\blank; \hat{a}_{1,n}(\data_n), \hat{a}_{2,n}(\data_n),
        \hat{b}_n(\data_n), \hat{\pi}_n(\data_n))]}.
  \end{split}
\end{equation}

@@

% We start by recalling some notation. We use \( F \) to denote a function that
% describes the conditional state occupation probabilities of the observed data,
% as defined in equation~(5) of the main paper. We denote the integrated Brier
% score as \( \bar B_\tau( F,O) = \int_0^{\tau} B_t(F,O) \diff t \), where
% \( B_t \) is defined
% \begin{equation*}
%   B_t(F,O) = \sum_{j=-1}^{2}
%   \left(
%       F(t,j,X) - \1{\{\eta(t)=j\}}
%   \right)^2.
% \end{equation*}
% Finally, recall that we let $\mathcal{H}_{\mathcal{P}}$ denote the function
% space consisting of all conditional state occupation probability functions for
% some measure \( P \in \mathcal{P} \), and that we equipped this space with the
% norm
% \begin{equation}
%   \label{eq:norm}
%   \| F \|_{P_0} = 
%   \left\{
%     \sum_{j=-1}^{2}\int_{\mathcal{X}} \int_0^{\tau} F(t, j, x)^2 \diff t H_0( \diff x)
%   \right\}^{1/2},
% \end{equation}
% for some fixed measure \( P_0 \in \mathcal{P} \). We use \( F_0 \) to denote the
% conditional state occupation probability function associated with the measure
% \( P_0 \).

>>>>

\institute{Anders Munch \at
              Section of Biostatistics, University of Copenhagen, Denmark \\
              % Tel.: +123-45-678910\\
              % Fax: +123-45-678910\\
              \email{a.munch@sund.ku.dk}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
              \and %
              Thomas~A.~Gerds %
              \at Section of Biostatistics, University of Copenhagen, Denmark}

@@

We introduce our notation and framework in Section~\ref{sec:framework}. In
Section~\ref{sec:super-learning} we define general super learning for
right-censored data. Section~\ref{sec:super-learner-simple} introduces the state
learner, and Section~\ref{sec:theor-results-prop} provides theoretical
guarantees. In Section~\ref{sec:targeted-learning} we discuss the use of the
state learner in the context of targeted learning. We report results of our
numerical experiments in Section~\ref{sec:numer-exper} and analyse a prostate
cancer data set in Section~\ref{sec:real-data-appl}.
Section~\ref{sec:discussion} contains a discussion of the merits and limitations
of our proposal. Proofs are given in Appendix~\ref{sec:proofs}. An
implementation of the state learner is available at
\url{https://github.com/amnudn/statelearner} along with code for reproducing our
numerical experiments.

@@

@@

for all \( t \in [0,\tau] \), \( k \in \{-1,0,1,2\} \), and \( x \in \mathcal{X} \).

@@

@@

      P{\big[
      \int_0^{\tau} \int_0^{s} w^a_n(s,u,\blank) [F - \hat{F}_n](u-, 0,
       \blank)[F - \hat{F}_n](s-, 0, \blank)}
    & \qquad \quad \times F(\diff u, -1, \blank ) F ( \diff s, 1, \blank)
      \big]

@@

An example of a targeted estimator is the one-step estimator, defined as
\begin{equation}
    \label{eq:one-step-def}
    \begin{split}
      \hat{\Psi}_{\text{OS}}(\data_n)
      = &
          \tilde{\Psi}^0(\hat{a}_{1,n}(\data_n), \hat{a}_{2,n}(\data_n),
          H_n(\data_n))
      \\
        & + \empmeas{[\psi(\blank; \hat{a}_{1,n}(\data_n), \hat{a}_{2,n}(\data_n),
          \hat{b}_n(\data_n) )]},
    \end{split}
\end{equation}
where \( \empmeas \) is the empirical measure of a data set
\(\{O_i\}_{i=1}^n\).
Under suitable regularity conditions
we have the
following asymptotic expansion of the one-step estimator
\citep{pfanzagl1985contributions,van2003unified,fisher2021visually,kennedy2022semiparametric},
\begin{equation*}
  \hat{\Psi}_{\text{OS}}(\data_n)- \Psi(P)
  =  \empmeas{[\psi(\blank ; \Lambda_1, \Lambda_2, \Gamma)]}
  +\mathrm{Rem}{(\hat{\Lambda}_{1,n},\hat{\Lambda}_{2,n},  \hat{\Gamma}_n, P)} + \smallO_{P}(n^{-1/2}),
\end{equation*}
where the remainder term has the form
\begin{equation}
  \label{eq:4}
  \mathrm{Rem}{(\hat{\Lambda}_{1,n},\hat{\Lambda}_{2,n},  \hat{\Gamma}_n, P)}
  = \bigO_P{
    \left\{
      \|\Lambda_1-\hat{\Lambda}_{1,n}\|^2
      +
      \|\Lambda_2-\hat{\Lambda}_{2,n}\|^2
      +
      \|\Gamma-\hat{\Gamma}_{n}\|^2
    \right\}
  },
\end{equation}
for some suitable norm \( \|\blank \| \), for instance the
\( \mathcal{L}_{P}^2 \)-norm. When equation~(\ref{eq:4}) holds and the
nuisance parameters $\Lambda_1$, $\Lambda_2$, and $\Gamma$ are
consistently estimated at rate \( \smallO_P{(n^{-1/4})} \), then
\begin{equation}
  \label{eq:3}
  \sqrt{n}(\hat{\Psi}_{\text{OS}}(\data_n)- \Psi(P)) \weakly \mathcal{N}(0,
  P{[\psi(\blank; \Lambda_1, \Lambda_2, \Gamma)^2]}),
\end{equation}
where we use \( \weakly \) to denote weak convergence \citep{van2000asymptotic}.
In particular, equation~(\ref{eq:3}) and Slutsky's lemma imply that we can
obtain asymptotically valid \((1-\alpha)\cdot100\%\) confidence intervals by
calculating
\begin{equation*}
  \left[
    \hat{\Psi}_{\text{OS}}(\data_n) - q_{\alpha/2} \hat{\sigma}(\data_n) ,
    \;
    \hat{\Psi}_{\text{OS}}(\data_n) + q_{\alpha/2} \hat{\sigma}(\data_n)
  \right],
\end{equation*}
where \( q_{\alpha} \) is the \( (1-\alpha) \)-quantile of the standard normal
distribution and
\begin{equation*}
  \hat{\sigma}(\data_n)^2 = \empmeas{ \left[ \psi(\blank;
      \hat{a}_{1,n}(\data_n), \hat{a}_{2,n}(\data_n), \hat{b}_n(\data_n))^2
    \right]}.
\end{equation*}

@@

In the following we detail how the state learner can be used to
construct a targeted estimator of the cause-specific average treatment
effect \citep{rytgaard2022targeted}. We assume that the covariate
vector \( X \in \R^p \) contains a binary treatment indicator \( A \)
and a vector of potential confounders,
\( W \in \mathcal{W}\subset \R^{p-1} \).  We use $\mu$ to denote the
marginal distribution of \( W \) and $\pi$ to denote the conditional
probability of treatment,
\begin{equation*}
  \pi(w) = P(A=1 \mid W=w).
\end{equation*}
We assume throughout that $\pi$ is uniformly bounded away from \( 0 \)
and \( 1 \) on \( \mathcal{W} \) and that both \( A \) and \( W \) are
fully observed for all individuals. We use a super learner to
estimate $\pi$ \citep{Polley_Ledell_Kennedy_Laan_2023_Superlearn}, and
we denote this estimator by $\hat{\pi}_n$. We use the empirical
measure of \( \{W_1, \dots, W_n\} \) to estimate $\mu$, and denote
this estimator by $\hat{\mu}_n$. As parameter of interest we consider
the standardised difference in the absolute risk of an event with
cause 1 at time $\tau$:
\begin{align*}
  & \theta_{{\tau}}(Q)
  \\
  & = \int_{\mathcal{W}} 
    \left\{
    \int_0^{\tau}
    S(s- \mid w, 1)  \Lambda_1(\diff s \mid w, 1)
    -
    \int_0^{\tau}
    S(s- \mid w, 0)  \Lambda_1(\diff s \mid w, 0)
    \right\}
    \mu(\diff w).
\end{align*}
Under the usual assumptions for causal inference (consistency,
positivity, no unmeasured confounding) \( \theta_{{\tau}} \) can be
given the causal interpretation
\begin{equation*}
  \theta_{{\tau}}(Q) =
  P{(T^{1} \leq \tau, D^{1}=1)}-
  P{(T^{0} \leq \tau, D^{0}=1)},
\end{equation*}
where \( (T^a, D^a) \), \( a \in \{0,1\} \), denote potential outcomes
\citep{hernanRobinsWhatIf}. In this case, the interpretation of $\theta_{\tau}$
is the difference in the average risk of cause \( 1 \) occurring before time
\( \tau \) in the population if everyone had been given treatment (\( A=1 \))
compared to if no one had been given treatment \( (A=0) \).

Using equation~(\ref{eq:surv-def}) we may write
\( \theta_{{\tau}}(Q) = \tilde{\Psi}_{\tau}^0(\Lambda_1, \Lambda_2, \mu) \), where
\begin{equation}
  \label{eq:1}    
  \begin{split}
    & \tilde{\Psi}_{\tau}^0(\Lambda_1, \Lambda_2, \mu)
    \\
    & =
      \int_{\mathcal{W}} 
      \int_0^{\tau}
      \exp{\{{-\Lambda_1(s- \mid w, 1)-\Lambda_2(s- \mid w, 1)}\}}  \Lambda_1(\diff s \mid
      w, 1)
      \mu(\diff w)
    \\
    &  \quad
      -\int_{\mathcal{W}} 
      \int_0^{\tau}
      \exp{\{{-\Lambda_1(s- \mid w, 0)-\Lambda_2(s- \mid w, 0)}\}}  \Lambda_1(\diff s \mid w, 0)
      \mu(\diff w).
  \end{split}
\end{equation}
The efficient influence function for the parameter $\tilde{\Psi}_{\tau}$ depends
on the set \( (\Lambda_1, \Lambda_2, \Gamma, \pi) \) of nuisance parameters.
We define
\begin{align*}
  \omega_a(A,W; \pi)
  &=  \frac{% (-1)^{a+1}
    \1{\{A=a\}}}{\pi(W)^{a}(1-\pi(W))^{1-a}},
  \\
  g(t, A, W; \Lambda_1, \Lambda_2)
  & = \int_0^{t}
    \exp{\{ {-\Lambda_1(s- \mid W, A)-\Lambda_2(s- \mid W, A)} \}}  \Lambda_1(\diff s \mid
    W, A),
  \\  
  M_j(\diff t \mid A, W;  \Lambda_j  )
  & = N_j(\diff t) -
    \1{\{\tilde{T} \geq t\}} \Lambda_j(\diff t \mid W, A),
    \quad j \in \{1,2\},
    \intertext{and}
    M(\diff t \mid A, W;  \Lambda_1, \Lambda_2  )
  & = M_1(\diff t \mid A, W;  \Lambda_1  ) +
    M_2(\diff t \mid A, W;  \Lambda_2  ).
\end{align*}
The efficient influence function can now be written as
\citep{van2003unified,jewell2007non,rytgaard2022targeted},
\begin{equation*}
  \psi_{\tau}(O; \Lambda_1, \Lambda_2, \Gamma, \pi)
  = \psi_{\tau}^1(O; \Lambda_1, \Lambda_2, \Gamma, \pi)
  - \psi_{\tau}^0(O; \Lambda_1, \Lambda_2, \Gamma, \pi)
  -\tilde{\Psi}_{\tau}^0(\Lambda_1, \Lambda_2, \mu),
\end{equation*}
where
\begin{equation}
  \label{eq:5}
  \begin{split}
    & \psi_{\tau}^a(O; \Lambda_1, \Lambda_2, \Gamma, \pi)
    \\
    & =
      \omega_a(A,W; \pi)
      \int_0^{\tau} \exp{\{{\Gamma(t- \mid A, W)}\}}   
      M_1(\diff t \mid A, W; \Lambda_1)
    \\
    & \quad
      -
      \omega_a(A,W; \pi)
      g(\tau, A, W; \Lambda_1, \Lambda_2)
    \\
    & \quad \quad \times
      \int_0^{\tau}
      \exp{\{{[\Gamma+\Lambda_1 + \Lambda_2](t- \mid A, W)}\}}
      M(\diff t \mid A, W; \Lambda_1, \Lambda_2)
    \\
    & \quad
      +
      \omega_a(A,W; \pi)      
      \int_0^{\tau}
      g(t, A, W; \Lambda_1, \Lambda_2)
    \\
    & \quad \quad \times
      \exp{\{{[\Gamma+\Lambda_1 + \Lambda_2](t- \mid A, W)}\}}
      M(\diff t \mid A, W; \Lambda_1, \Lambda_2)
    \\
    & \quad + g(\tau, a, W; \Lambda_1, \Lambda_2).
  \end{split}
\end{equation}
Equations~(\ref{eq:1}) and~(\ref{eq:5}) allow us to construct a one-step
estimator by using the definition given in equation~(\ref{eq:one-step-def}),
which gives the estimator
\begin{equation}
  \label{eq:one-step-comp-ate}
  \begin{split}
    \hat{\Psi}_{\tau,\text{OS}}(\data_n)
    = &
        \tilde{\Psi}_{\tau}^0(\hat{a}_1(\data_n), \hat{a}_2(\data_n),
        \hat{\mu}_n(\data_n))
    \\
      &
        +
        \empmeas{[\psi_{\tau}(\blank; \hat{a}_{1,n}(\data_n), \hat{a}_{2,n}(\data_n),
        \hat{b}_n(\data_n), \hat{\pi}_n(\data_n))]}
    \\
    = &
        \empmeas{[\psi_{\tau}^1(\blank; \hat{a}_{1,n}(\data_n), \hat{a}_{2,n}(\data_n),
        \hat{b}_n(\data_n), \hat{\pi}_n(\data_n))]}
    \\
      &
        - \empmeas{[\psi_{\tau}^0(\blank; \hat{a}_{1,n}(\data_n), \hat{a}_{2,n}(\data_n),
        \hat{b}_n(\data_n), \hat{\pi}_n(\data_n))]}.
  \end{split}
\end{equation}

@@
